Light Curves \& Planet Candidates in Open Clusters from TESS Sectors 6 \& 7

### 2019-07-10 paper/ms.tex
minor paper update

In our photometric reduction,  our default identifier for all sources
is the Gaia-DR2 \texttt{source\_id}.
The TIC identifiers are found through a spatial cross-match after the light 
curves have been made
\citep{stassun_TIC_2018,stassun_TIC8_2019}
This is because Gaia-DR2 is the base-catalog used to project
sources from celestial coordinates to the imaging plane (\S~\ref{sec:method}).
It also has the advantage that for any Gaia-derived cluster memberships, 
we preform cross-matching directly via the source identifiers.

@@

\begin{figure*}[!h]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page01.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Page 1: period-search summary.} Periodograms from TLS and 
		phase-dispersion minimization, as calculated 
		with \texttt{astrobase.periodbase}, are shown in the top left and top center 
		\citep{bhatti_astrobase_2018,hippke_TLS_2019,stellingwerf_period_1978}.
		The top three peaks from each 
		method are shown in the second and third rows; the raw light curve is in the 
		top-right. A small finder chart from DSS is inset to the top left, with
		the 1.5-pixel radius aperture used to extract the light curve in orange (CITE).
		\label{fig:pg1}
	}
\end{figure*}

\begin{figure*}[!h]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page02.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Page 2: light curve diagnostics.} 
		Time-series of raw flux (\texttt{IRM2}),  TFA-detrended flux (\texttt{TF2}), stellar-variability
		detrended flux, and the background are shown as a function of
		barycentric Julian date.
		The overplotted dashed vertical lines are the ephemeris of the highest-power
		TLS peak from Figure~\ref{fig:pg1}.
		An important check is whether the flux dips are correlated with changes in the 
		background level -- in this case, they are not.
		The standard deviation and TESS magnitude are quoted in the upper right.
		The red line in the second from the top plot is the windowed 
		spline described in Section~\ref{subsec:ctois} -- in this case it is near its maximal
		frequency.
		\label{fig:pg2}
	}
\end{figure*}

\begin{figure*}[!h]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page03.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    {\bf Page 3: Transit diagnostics.} The plots show the
    maximally-detrended light curve (top); the phase-folded light
    curve centered over $\pm3$ transit durations of the primary
    transit (middle left); the secondary eclipse (middle right); the
    odd-numbered transits (lower left); and the even-numbered transits
    (lower right).
    The stellar parameters ($T_{\rm eff}, R_\star$) are taken from
    Gaia-DR2 Apsis pipeline results when available
    \citep{andrae_apsis_2018}.
    The first eight lines of text are parameters determined from the
    best-fitting TLS model.
    The one exception is the planet radius, which uses the stellar
    radius as noted above.
    The ``flux contamination'' (\texttt{TICCONT}) from neighboring
    stars is {\it never} taken into account, because transit depth
    dilution does not affect image subtraction analyses in the same
    manner as aperture-photometry reductions.
    To estimate the transit to occulation depth ratio, the
    phase-folded light curve is also coarsely fit via maximum
    likelihood by a sum of two gaussians.
    ``AstExc'' refers to the Gaia-DR2 astrometric excess, which can
    indicate hints of astrometric binarity in the system.
    ``$R_\star + M_\star \rightarrow T_{b0}$'' gives the duration of a
    zero-eccentricity central transit based on the Gaia-DR2 stellar
    radius, and a stellar mass interpolated from the
    \citet{pecaut_intrinsic_2013} table, under the assumption that the
    star is a dwarf.
    %\footnote{\url{http://www.pas.rochester.edu/~emamajek/EEM_dwarf_UBVIJHK_colors_Teff.txt}}.
		\label{fig:pg3}
	}
\end{figure*}

\begin{figure*}[!h]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page04.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Page 4: Light curves for increasing aperture sizes.} 
		Apertures of radius 1, 1.5, and 2.25 pixels are shown from top to bottom.
		The blue line is the reference transit depth from the best-fitting TLS model.
		Any changes in depth with aperture size might indicate the need for a 
		detailed pixel-level analysis.
		\label{fig:pg4}
	}
\end{figure*}

\begin{figure*}[!h]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page05.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Page 5: Cluster membership assessment diagnostics.}
		The star was considered a candidate cluster member by the source(s) listed under
		``Reference'', in this case \citet{dias_proper_2014}.
		The name used in the Dias catalog in this case was \texttt{264-025831}, a
		UCAC-4 identifier, which can be back-referenced to find that \citet{dias_proper_2014}
		assigned this star a
		membership probability in NGC 2546 of 98\%.
		The base catalog for the plots is chiefly that of \citet{Kharchenko_et_al_2013},
		due to its homogeneous parameter determination procedure (particularly for age).
		If a match to the \citet{Kharchenko_et_al_2013} catalog is found, then the remaining
		plots are populated.
		Top-left shows the parallax, with orange points sampled from the Gaia-DR2
		posterior, black points the other cluster members in the Kharchenko catalog,
		and the blue line the claimed Kharchenko parallax for the cluster.
		A large number of field contaminants are visible in this case.
		Top-right are the Gaia proper motions, where against black points are cluster
		members from Kharchenko, and the orange is the target star.
    Bottom-left is the color-magnitude diagram, and bottom-right are
    the on-sky positions.  In the text,
		\texttt{N1sr2} is the number of $1\sigma$ cluster members reported
		by \citet{Kharchenko_et_al_2013} within the cluster angular radius;
		$\log t$ is the base-10 logarithm of the age in years;
		\texttt{type} matches the type codes provided by
    \citet{Kharchenko_et_al_2013};
    \texttt{K13Note} gives the description of the cluster from
    \citet{Kharchenko_et_al_2013}, if available.
		\label{fig:pg5}
	}
\end{figure*}

\begin{figure*}[!h]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page06.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Page 6: Imaging variability diagnostics.} 
		This page is intended to help diagnose which stars are producing the observed
		variability.
		Top-left and top-center are the mean out-of-transit (OOT) and mean in-transit 
		calibrated images (separate from any of our image-subtraction analysis).
		The OOT images are based on the same number of exposures as the in-transit images
		and split evenly before and after each transit \citep[following][]{bryson_identification_2013,kostov_l9859_2019}.
		The yellow star is the target; cyan dots are the flux-weighted centroid of the entire
		image for each transit event; small red crosses are WCS-projected locations of neighbor stars.
		Middle-left is the most important sub-panel: the difference between
		the OOT and in-transit mean images.
		If the variability shown in background map (units: ADU) is off-target, the
		transit is typically not from the target star.
		Middle-center is the same, normalized by the uncertainty map.
		Lower left and lower center show the DSS field in linear and log scales
		at roughly the same pixel scale as the TESS image,
		with the 1, 1.5, and 2.25 pixel-radius apertures in blue, orange, and green respectively.
		The brightness of neighborhood stars is given on the far right.
		Note the slight rotation difference between DSS and TESS images;
		DSS images are aligned north-up, east-left; TESS images are oriented as closely as
		possible to this system without actually performing the rotation.
		\label{fig:pg6}
	}
\end{figure*}

>>>>

In our photometric reduction,  our default identifier for all sources
is the Gaia-DR2 \texttt{source\_id}.  The TIC identifiers are found
through a spatial cross-match after the light curves have been made,
subject to the requirement that the Gaia-DR2 source identifiers match
\citep{stassun_TIC_2018,stassun_TIC8_2019}.  We take this approach
because Gaia-DR2 is the base-catalog used to project sources from
celestial coordinates to the imaging plane (\S~\ref{sec:method}).  It
also has the advantage that for any Gaia-derived cluster memberships,
we can cross-match directly against source identifiers.

@@

\begin{figure*}[!h]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page01.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Transit search summary.} Periodograms from TLS and 
		phase-dispersion minimization, as calculated 
		with \texttt{astrobase.periodbase}, are shown in the top left and top center 
		\citep{bhatti_astrobase_2018,hippke_TLS_2019,stellingwerf_period_1978}.
		The top three peaks from each 
		method are shown in the second and third rows; the raw light curve is in the 
		top-right. A small finder chart from DSS is inset to the top left, with
		the 1.5-pixel radius aperture used to extract the light curve in orange.
		\label{fig:pg1}
	}
\end{figure*}

\begin{figure*}[!h]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page02.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Light curve diagnostics.} 
		Time-series of raw flux (\texttt{IRM2}),  TFA-detrended flux (\texttt{TF2}), stellar-variability
		detrended flux, and the background are shown as a function of
		barycentric Julian date.
		The overplotted dashed vertical lines are the ephemeris of the highest-power
		TLS peak from Figure~\ref{fig:pg1}.
		An important check is whether the flux dips are correlated with changes in the 
		background level -- in this case, they are not.
		The standard deviation and TESS magnitude are quoted in the upper right.
		The red line in the second from the top plot is the windowed 
		spline described in Section~\ref{subsec:ctois} -- in this case it is near its maximal
		frequency.
		\label{fig:pg2}
	}
\end{figure*}

\begin{figure*}[!h]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page03.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    {\bf Transit diagnostics.} The plots show the
    maximally-detrended light curve (top); the phase-folded light
    curve centered over $\pm3$ transit durations of the primary
    transit (middle left); the secondary eclipse (middle right); the
    odd-numbered transits (lower left); and the even-numbered transits
    (lower right).
    The stellar parameters ($T_{\rm eff}, R_\star, M_\star$) are taken from
    TICv8 when available \citep{stassun_TIC8_2019}.
    %Gaia-DR2 Apsis pipeline results when available
    %\citep{andrae_apsis_2018}.
    The first eight lines of text are parameters determined from the
    best-fitting TLS model.
    The one exception is the planet radius, which uses the stellar
    radius as noted above.
    The ``flux contamination'' (\texttt{TICCONT}) from neighboring
    stars is {\it never} taken into account, because transit depth
    dilution does not affect image subtraction analyses in the same
    manner as aperture-photometry reductions.
    To estimate the transit to occulation depth ratio, the
    phase-folded light curve is also coarsely fit via maximum
    likelihood by a sum of two gaussians.
    ``AstExc'' refers to the Gaia-DR2 astrometric excess, which can
    indicate hints of astrometric binarity in the system.
    ``$d_{\rm geom}$'' is the geometric distance from
    \citet{bailer-jones_distances_2018}.
    ``$R_\star + M_\star \rightarrow T_{b0}$'' gives the duration of a
    zero-eccentricity central transit based on the TICv8 stellar
    radius and mass if available. If the mass is not available, a
    stellar mass is interpolated from the
    \citet{pecaut_intrinsic_2013} table, under the assumption that the
    star is a dwarf.
    %\footnote{\url{http://www.pas.rochester.edu/~emamajek/EEM_dwarf_UBVIJHK_colors_Teff.txt}}.
		\label{fig:pg3}
	}
\end{figure*}

\begin{figure*}[!h]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page04.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Light curves for increasing aperture sizes.} 
		Apertures of radius 1, 1.5, and 2.25 pixels are shown from top to bottom.
		The blue line is the reference transit depth from the best-fitting TLS model.
		Any changes in depth with aperture size might indicate the need for a 
		detailed pixel-level analysis.
		\label{fig:pg4}
	}
\end{figure*}

\begin{figure*}[!h]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page05.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Cluster membership assessment diagnostics.}
		The star was considered a candidate cluster member by the source(s) listed under
		``Reference'', in this case \citet{dias_proper_2014}.
		The name used in the Dias catalog in this case was \texttt{264-025831}, a
		UCAC-4 identifier, which can be back-referenced to find that \citet{dias_proper_2014}
		assigned this star a
		membership probability in NGC 2546 of 98\%.
		The base catalog for the plots is chiefly that of \citet{Kharchenko_et_al_2013},
		due to its homogeneous parameter determination procedure (particularly for age).
		If a match to the \citet{Kharchenko_et_al_2013} catalog is found, then the remaining
		plots are populated.
		Top-left shows the parallax, with orange points sampled from the Gaia-DR2
		posterior, black points the other cluster members in the Kharchenko catalog,
		and the blue line the claimed Kharchenko parallax for the cluster.
		A large number of field contaminants are visible in this case.
		Top-right are the Gaia proper motions, where against black points are cluster
		members from Kharchenko, and the orange is the target star.
    Bottom-left is the color-magnitude diagram, and bottom-right are
    the on-sky positions.  In the text,
		\texttt{N1sr2} is the number of $1\sigma$ cluster members reported
		by \citet{Kharchenko_et_al_2013} within the cluster angular radius;
		$\log t$ is the base-10 logarithm of the age in years;
		\texttt{type} matches the type codes provided by
    \citet{Kharchenko_et_al_2013};
    \texttt{K13Note} gives the description of the cluster from
    \citet{Kharchenko_et_al_2013}, if available.
		\label{fig:pg5}
	}
\end{figure*}

\begin{figure*}[!h]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.98\textwidth]{gaiatwo0005541111035713815552-0007_page06.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Imaging variability diagnostics.} 
		This page is intended to help diagnose which stars are producing the observed
		variability.
		Top-left and top-center are the mean out-of-transit (OOT) and mean in-transit 
		calibrated images (separate from any of our image-subtraction analysis).
		The OOT images are based on the same number of exposures as the in-transit images
		and split evenly before and after each transit \citep[following][]{bryson_identification_2013,kostov_l9859_2019}.
		The yellow star is the target; cyan dots are the flux-weighted centroid of the entire
		image for each transit event; small red crosses are WCS-projected locations of neighbor stars.
		Middle-left is the most important sub-panel: the difference between
		the OOT and in-transit mean images.
		If the variability shown in background map (units: ADU) is off-target, the
		transit is typically not from the target star.
		Middle-center is the same, normalized by the uncertainty map.
		Lower left and lower center show the DSS field in linear and log scales
		at roughly the same pixel scale as the TESS image,
		with the 1, 1.5, and 2.25 pixel-radius apertures in blue, orange, and green respectively.
		The brightness of neighborhood stars is given on the far right.
		Note the slight rotation difference between DSS and TESS images;
		DSS images are aligned north-up, east-left; TESS images are oriented as closely as
		possible to this system without actually performing the rotation.
		\label{fig:pg6}
	}
\end{figure*}
